### 2012-07-12 developing mind/chapter_01.tex
working
working on proposal

\def \ititle {The Developing Mind}
\def \isubtitle {}
\def \iauthor {Stephen A. Butterfill}
\def \iemail{s.butterfill@warwick.ac.uk}
%\def \iauthor {}
%\def \iemail{}
\date{}

@@

How do humans come to know  about---and to knowingly manipulate---%
objects,
causes,
words,
numbers,
colours,
actions
and
thoughts?
In a beautiful myth, Plato suggests that the answer is recollection. 
Before birth, in another world, we become acquainted with the truth. 
Then, in falling to earth, we forget everything. 
But as we grow we are sometimes able to recall part of what we once knew.
So it is by recollection that humans come to know about objects, causes, numbers and everything else.

@@

In broad outline, then, understanding the developmental origins of knowledge calls detailed investigation of many interacting but separate phenomena rather than large-scale theory building. 
This attitude is nicely captured by some psychologists reflecting on difficulties in understanding knowledge of objects:
%
\begin{quote}
`there are many separable systems of mental representations ...\ and thus many different kinds of knowledge. ...\ the task ...\ is to contribute to the enterprise of finding the distinct systems of mental representation and to understand their development and integration% 
%. ...\ the challenge ...\ is to characterize what it is about the mental representations of the presence or absence of the barriers that constrains representations of where the object should be in looking-time studies and how these representations differ from those that guide search or pointing in the present studies%
'
\citep[p.\ 1522]{Hood:2000bf}.
\end{quote}
%
%obstacle --- half-formed minds
Performing this task  requires philosophical as well as more narrowly psychological investigation. 
The question is how humans come to know about objects, words, thoughts and other things. 
In pursuing this question we have to consider minds where the knowledge is neither clearly present nor obviously absent. 
This is challenging because both commonsense and theoretical tools for describing minds are generally designed for characterising fully developed adults. 
Davidson writes:
%
\begin{quote}
`%
%if you want to describe what is going on in the head of the child when it has a few words which it utters in appropriate situations, you will fail for lack of the right sort of words of your own. 
We have many vocabularies for describing nature when we regard it as mindless, and we have a mentalistic vocabulary for describing thought and intentional action; what we lack is a way of describing what is in between' \citep[p.\ 11]{Davidson:1999ju}.
\end{quote}
%
%Of course you might not agree with Davidson that children just starting to use words are incapable of thought or of intentional action. 
%In fact research on children's pre-verbal communicative behaviours such as pointing seems not only to manifest purposiveness but also a sensitivity to others' thoughts.
%(Davidson seems to have paid little attention to development, and he held that being able to think, to act intentionally and to communicate with language all require understanding the possibility that one's own beliefs may be false.)
%Even so, Davidson 
%
This is why philosophy is needed. 
To understand the emergence of knowledge we need to find ways of describing what is in between: individuals whose movements are neither mindless nor guided by intention and knowledge.  
%in between ways of describing individuals, ways that neither treat them as mindless nor presuppose capacities for knowledge.

@@

%source!
%research/Development as Rediscovery--core knowledge and speech perception.doc

>>>>

\def \ititle {The Developing Mind: }
\def \isubtitle {A philosophical introduction to issues in cognitive development}
\def \iauthor {Stephen A. Butterfill}
\def \iemail{s.butterfill@warwick.ac.uk}
%\def \iauthor {}
%\def \iemail{}
\date{}

@@

How do humans come to know  about---and to knowingly manipulate---%
objects,
causes,
words,
numbers,
colours,
actions
and
minds?
In a beautiful myth, Plato suggests that the answer is recollection. 
Before birth, in another world, we become acquainted with the truth. 
Then, in falling to earth, we forget everything. 
But as we grow we are sometimes able to recall part of what we once knew.
So it is by recollection that humans come to know about objects, causes, numbers and everything else.

@@

%obstacle --- half-formed minds
Performing this task  requires philosophical as well as more narrowly psychological investigation. 
The question is how humans come to know about objects, words, thoughts and other things. 
In pursuing this question we have to consider minds where the knowledge is neither clearly present nor obviously absent. 
This is challenging because both commonsense and theoretical tools for describing minds are generally designed for characterising fully developed adults. 
Davidson writes:
%
\begin{quote}
`%
%if you want to describe what is going on in the head of the child when it has a few words which it utters in appropriate situations, you will fail for lack of the right sort of words of your own. 
We have many vocabularies for describing nature when we regard it as mindless, and we have a mentalistic vocabulary for describing thought and intentional action; what we lack is a way of describing what is in between' \citep[p.\ 11]{Davidson:1999ju}.
\end{quote}
%
%Of course you might not agree with Davidson that children just starting to use words are incapable of thought or of intentional action. 
%In fact research on children's pre-verbal communicative behaviours such as pointing seems not only to manifest purposiveness but also a sensitivity to others' thoughts.
%(Davidson seems to have paid little attention to development, and he held that being able to think, to act intentionally and to communicate with language all require understanding the possibility that one's own beliefs may be false.)
%Even so, Davidson 
%
This is why philosophy is needed. 
To understand the emergence of knowledge we need to find ways of describing what is in between: individuals whose movements are neither mindless nor guided by intention and knowledge.  
%in between ways of describing individuals, ways that neither treat them as mindless nor presuppose capacities for knowledge.

@@

\section{Core Knowledge and Perception}
%source!
%research/Development as Rediscovery--core knowledge and speech perception.doc

In broad outline, then, understanding the developmental origins of knowledge calls detailed investigation of many interacting but separate phenomena rather than large-scale theory building. 
This attitude is nicely captured by some psychologists reflecting on difficulties in understanding knowledge of objects:
%
\begin{quote}
`there are many separable systems of mental representations ...\ and thus many different kinds of knowledge. ...\ the task ...\ is to contribute to the enterprise of finding the distinct systems of mental representation and to understand their development and integration% 
%. ...\ the challenge ...\ is to characterize what it is about the mental representations of the presence or absence of the barriers that constrains representations of where the object should be in looking-time studies and how these representations differ from those that guide search or pointing in the present studies%
'
\citep[p.\ 1522]{Hood:2000bf}.
\end{quote}
%

\section{Development as rediscovery}

\section{Social Origins of Knowledge}
